\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}

\geometry{a4paper, margin=1in}
\title{Agile Project Management System - User Stories}
\author{Product Owner}
\date{\today}

\begin{document}

\maketitle

\section*{Epic: Project Setup}

\subsection*{US-001: Create New Project}
As a project manager, I want to create a new project with custom settings so that I can organize work according to project requirements.

\textbf{Acceptance Criteria:}
\begin{itemize}
    \item Verify that the "Create Project" button opens a configuration modal.
    \item Ensure custom settings include project name, start date, and team selection.
    \item Confirm that the project is saved to the database upon clicking "Save".
\end{itemize}

\subsection*{US-002: Assign Team Members}
As a project manager, I want to assign team members to projects so that they can start contributing to project tasks.

\textbf{Acceptance Criteria:}
\begin{itemize}
    \item Verify that a list of available team members is displayed.
    \item Ensure multiple members can be selected at once.
    \item Confirm that assigned members receive an email notification.
\end{itemize}

\section*{Epic: Task Management}

\subsection*{US-003: Create Task}
As a team member, I want to create tasks with clear descriptions so that everyone understands what needs to be done.

\textbf{Acceptance Criteria:}
\begin{itemize}
    \item Verify that the task creation form includes a rich-text description field.
    \item Ensure images can be embedded in the description.
    \item Confirm that the task cannot be saved without a title.
\end{itemize}

\subsection*{US-004: Set Task Priority}
As a team member, I want to set task priorities (high, medium, low) so that the team can focus on urgent work first.

\textbf{Acceptance Criteria:}
\begin{itemize}
    \item Verify that a priority flag can be toggled between High, Medium, and Low.
    \item Ensure High priority tasks are visually distinct (e.g., red color).
    \item Confirm that tasks can be sorted by priority in the list view.
\end{itemize}

\subsection*{US-005: Log Work Hours}
As a team member, I want to log time spent on tasks so that I can track effort and improve estimation accuracy.

\textbf{Acceptance Criteria:}
\begin{itemize}
    \item Verify that a timer can be started and stopped on a task.
    \item Ensure manual time entry is also supported.
    \item Confirm that total time spent is displayed against the estimate.
\end{itemize}

\end{document}
